Thickness optimization in wide range quasi omnidirectional 1-D photonic structures

### 2020-12-06 PaperVictor.tex
Remove end of lines
Add Acknowldgment to dgapa.
Revise abstract

\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaVCG}[1]{{\bf \em \color{orange}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayer structures, since high and low porosity layers
can be synthesized by simple electrochemical technique. We report the
maximization of average reflectance (R$_{\text{prom}}\left(\lambda,\theta%
\right)$) with minimum possible thickness of PS-based mirrors with different
porosity contrasts. Optimization is performed in two regions (Visible and
NIR) of the electromagnetic spectrum. We employ two techniques to design the
mirrors: \textit{chirped} structures and the \textit{stacking} of sub-mirrors. The
chirped structures were found to be relatively more suitable for obtaining
highly reflectivity in the visible range, while the second type of
structure was more effective for obtaining high reflectivity in the IR
region. Some of the optimized omnidirectional structures with less than 100
periods have been designed and experimentally demonstrated in a wide
spectral range.
\end{abstract}

@@

Photonic crystal (PC)-based structures are extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and 
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation will be limited by photonic band gaps (PBGs)
where transmission states are forbidden. The PC  shows a 
PBG corresponding to the electromagnetic modes which are not allowed to propagate
through the structure and behaves as a perfect mirror for that range. The width of
reflection spectrum is important while designing an omnidirectional mirror for 
different applications. The metallic mirrors are widely accepted for reflection 
purposes, but widespread use is limited due to their absorptive nature at the 
visible and near infrared frequencies.  A good alternative are dielectric
structures as they also provide design flexibility in terms of
reflection wavelength. These properties are widely used to design various
one-dimensional (1D) and two-dimensional (2D) PCs for its
potential applications in optoelectronics, optical telecommunications and computing, 
laser technology \cite{Lopez2013,Masaya2010}, and radiative cooling applications 
\cite{Kumar2020}. The simplest 1D PC is composed of alternating high $\left( 
n_{H}\right) $ and low $\left(n_{L}\right) $ refractive index layers (Bragg Mirror, 
BM). The optical thicknesses are typically chosen to be quarter-wavelength length, $
n_{H}d_{H}=n_{L}d_{L}=\lambda _{0}/4$, at some operating wavelength $\lambda
_{0}$ (center wavelength) to obtain a certain
omnidirectional band gap. As the gap depends on the contrast of the
refractive indices and the number of periods,  broadband mirrors can  be
engineered by modulating the reflection in a broader wavelength range.
One of the ways to obtain such structures has been the continuous variation of 
thicknesses along the depth, defined as \textit{chirped}-type \cite{Zipock1997} 
structures. Additionally, broader mirrors can also be achieved by overlapping 
different BMs, where each one reflects around a specific central wavelength, 
resulting in a wider photonic band gap \cite{Xifre2009}.

Till now, different deposition techniques have been used to obtain omnidirectional 
BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
electromagnetic spectrum. For example, Chen et al., \cite{Chen1999} have
reported an ODBM of about 70 nm in NIR range designed with 6-pairs  of 
TiO$_{2}$/SiO$_{2}$ deposited using sol-gel method. Park et al., \cite{Park2003} 
used molecular beam epitaxy to grow a stack of four pairs of GaAs$/$AlAs layers, 
followed by its conversion to a multilayer stack of GaAs/Al$_{2}$O$_{3}$ by selective
oxidation of the AlAs layers, to obtain an ODBM with a gap from 710 to 950
nm. On the other hand, DeCorby et al., \cite{DeCorby2005} fabricated mirrors by 
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting 
respectively, to obtain 150 nm wide omnidirectional band, centered at 1750 nm 
wavelength. Furthermore, Jena et al., \cite{Jena2016}
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate 1DPC of TiO$_{2}$/SiO$_{2}$ and achieved ODBM from
592 to 668 nm. However, these techniques are expensive and
require sophisticated equipment and long fabrication time. Using porous silicon (PS) 
is an alternative, as PS is typically fabricated by simple electrochemical etching of
crystalline Si in hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air in a relatively short duration of 
time. The generated porosity can be tuned by changing the applied current
density and hence modifies the refractive index of the resulting PS. This
fact opens the possibility of designing 1DPC with PS, which seeks to
control the propagation of light in a dielectric medium. The low cost and
ease of obtaining porous silicon make it an excellent candidate to develop
optical devices based on multilayer structures \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of porous silicon, they have been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
photoluminescence control \cite{Antunez2014}. Recently, the study of 
quasi-omnidirectional Bragg mirrors has increased due to their possible application 
as a flat lens \cite{Kozar2017,Cheng2018}. In particular, PS based dielectric 
optical filters, quasi-ODBM and ODBM have been extensively studied in different 
regions of the electromagnetic spectrum, such as ultraviolet (UV) 
\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR) \cite{Bruyant2003}. Keeping 
in view that high values of average porosity, refractive index contrast and 
thickness make the multilayer structures fragile, in this work various wide
band gap photonic structures have been proposed to obtain maximal average 
reflectance (R$_{\text{ave}}\left( \lambda ,\theta \right) $) with the minimum 
possible thickness and low refractive index contrast.

@@

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, p-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions 
\cite{Canham90,Escorcia07}. Electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous HF (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
With this electrolyte, the minimum and maximum porosities that can be
obtained are 35$\%$ and 76$\%$ (gravimetrically obtained), using current densities of 0.5 and 305 mA$/$%
cm$^{2}$, respectively. However, it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte diffusivity problems \cite{Ariza2011}. 
For this reason, the current
densities were chosen as 35 and 305 mA$/$cm$^{2}$, with corresponding
porosities of 51$\%$ and 76$\%$, respectively. The calibration curves were
acquired through a gravimetric technique as follows: single layers of porous
silicon were synthesized under similar conditions and were weighed ($m_{i}$)
before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
dissolving the already formed porous silicon layer ($m_{3}$), to calculate
the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Brugeman2006}. Etching
rate of PS was obtained by re-synthetizing individual layers under similar
conditions and measuring their thicknesses through scanning electron
microscopy (SEM). The absolute reflectivity measurements were carried out
with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
angle universal reflectance accessory (URA) for different incident angles $%
\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $%
50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
minimum values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

@@

\section*{Acknowledgments}
This work was partially supported by Consejo Nacional de Ciencia y Tecnolog\'{i}a through grant No. \textbf{256243} and C\'{a}tedras Conacyt program 1577.
%\end{acknowledgments}

@@

\bibitem{Lopez2013} C. L\'{o}pez, Materials aspects of photonic crystals, 
\textit{Adv. Mater.} \textbf{15}, 1679--1704 (2013).

@@

\bibitem{Jena2016} S. Jena, R.B. Tokas, S. Tripathi, K.D. Rao, D.V. Udupa,
S. Thakur, N.K. Sahoo Influence of oxygen partial pressure on
microstructure, optical properties, residual stress and laser induced damage
threshold of amorphous HfO2 thin films \textit{Journal of Alloys and
Compounds}, Volume 771, 2019, pp. 373-381

@@

\bibitem{Canham90} Canham L. T. Silicon quantum wire array fabrication by
electrochemical and chemical dissolution of wafers. \textit{Appl. Phys. Lett.%
}, 57(\textbf{10}):1046-1048, (1990).

\bibitem{Escorcia07} Escorcia J. and Agarwal V. E ect of duty cycle and
frequency on the morphology of porous silicon formed by alternating square
pulse anodic etching. \textit{Phys. Status Solidi (c)}, 4(\textbf{6}%
):2039-2043, (2007).

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\usepackage{braket}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaVCG}[1]{{\bf \em \color{orange}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. We
maximize the reflectance ($\braket{R}$ \notaL{El promedio no depende
  de lambda ni theta, y prom es castellano} averaged over a wide wavelength
and angular range  of PS-based mirrors with different
porosity contrasts searching for a minimum thickness. Optimization is
performed in the visible (Vis) and near infrarred (NIR) regions of the
electromagnetic spectrum. We design the mirrors using \textit{chirped}
structures and \textit{stacking} sub-mirrors. The
chirped structures were better suited for the Vis, and the stacked
sub-mirrors for the NIR regions. We design, fabricate and test some
optimized omnidirectional structures with less than 100
periods.
\end{abstract}

@@

Photonic crystal (PC)-based structures are extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation will be limited by photonic band gaps (PBGs)
where transmission states are forbidden. The PC  shows a
PBG corresponding to the electromagnetic modes which are not allowed to propagate
through the structure and behaves as a perfect mirror for that range. The width of
reflection spectrum is important while designing an omnidirectional mirror for
different applications. The metallic mirrors are widely accepted for reflection
purposes, but widespread use is limited due to their absorptive nature at the
visible and near infrared frequencies.  A good alternative are dielectric
structures as they also provide design flexibility in terms of
reflection wavelength. These properties are widely used to design various
one-dimensional (1D) and two-dimensional (2D) PCs for its
potential applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D PC is composed of alternating high $\left(
n_{H}\right) $ and low $\left(n_{L}\right) $ refractive index layers (Bragg Mirror,
BM). The optical thicknesses are typically chosen to be quarter-wavelength length, $
n_{H}d_{H}=n_{L}d_{L}=\lambda _{0}/4$, at some operating wavelength $\lambda
_{0}$ (center wavelength) to obtain a certain
omnidirectional band gap. As the gap depends on the contrast of the
refractive indices and the number of periods,  broadband mirrors can  be
engineered by modulating the reflection in a broader wavelength range.
One of the ways to obtain such structures has been the continuous variation of
thicknesses along the depth, defined as \textit{chirped}-type \cite{Zipock1997}
structures. Additionally, broader mirrors can also be achieved by overlapping
different BMs, where each one reflects around a specific central wavelength,
resulting in a wider photonic band gap \cite{Xifre2009}.

Till now, different deposition techniques have been used to obtain omnidirectional
BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
electromagnetic spectrum. For example, Chen et al., \cite{Chen1999} have
reported an ODBM of about 70 nm in NIR range designed with 6-pairs  of
TiO$_{2}$/SiO$_{2}$ deposited using sol-gel method. Park et al., \cite{Park2003}
used molecular beam epitaxy to grow a stack of four pairs of GaAs$/$AlAs layers,
followed by its conversion to a multilayer stack of GaAs/Al$_{2}$O$_{3}$ by selective
oxidation of the AlAs layers, to obtain an ODBM with a gap from 710 to 950
nm. On the other hand, DeCorby et al., \cite{DeCorby2005} fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain 150 nm wide omnidirectional band, centered at 1750 nm
wavelength. Furthermore, Jena et al., \cite{Jena2019}
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate 1DPC of TiO$_{2}$/SiO$_{2}$ and achieved ODBM from
592 to 668 nm. However, these techniques are expensive and
require sophisticated equipment and long fabrication time. Using porous silicon (PS)
is an alternative, as PS is typically fabricated by simple electrochemical etching of
crystalline Si in hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air in a relatively short duration of
time. The generated porosity can be tuned by changing the applied current
density and hence modifies the refractive index of the resulting PS. This
fact opens the possibility of designing 1DPC with PS, which seeks to
control the propagation of light in a dielectric medium. The low cost and
ease of obtaining porous silicon make it an excellent candidate to develop
optical devices based on multilayer structures \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of porous silicon, they have been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
photoluminescence control \cite{Antunez2014}. Recently, the study of
quasi-omnidirectional Bragg mirrors has increased due to their possible application
as a flat lens \cite{Kozar2017,Cheng2018}. In particular, PS based dielectric
optical filters, quasi-ODBM and ODBM have been extensively studied in different
regions of the electromagnetic spectrum, such as ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR) \cite{Bruyant2003}. Keeping
in view that high values of average porosity, refractive index contrast and
thickness make the multilayer structures fragile, in this work various wide
band gap photonic structures have been proposed to obtain maximal average
reflectance (R$_{\text{ave}}\left( \lambda ,\theta \right) $) with the minimum
possible thickness and low refractive index contrast.

@@

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, p-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. Electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous HF (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
With this electrolyte, the minimum and maximum porosities that can be
obtained are 35$\%$ and 76$\%$ (gravimetrically obtained), using current densities of 0.5 and 305 mA$/$%
cm$^{2}$, respectively. However, it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte diffusivity problems \cite{Ariza2011}.
For this reason, the current
densities were chosen as 35 and 305 mA$/$cm$^{2}$, with corresponding
porosities of 51$\%$ and 76$\%$, respectively. The calibration curves were
acquired through a gravimetric technique as follows: single layers of porous
silicon were synthesized under similar conditions and were weighed ($m_{i}$)
before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
dissolving the already formed porous silicon layer ($m_{3}$), to calculate
the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Brugeman2006}. Etching
rate of PS was obtained by re-synthetizing individual layers under similar
conditions and measuring their thicknesses through scanning electron
microscopy (SEM). The absolute reflectivity measurements were carried out
with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
angle universal reflectance accessory (URA) for different incident angles $%
\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $%
50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
minimum values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

@@

\section*{Acknowledgments}
This work was partially supported by Consejo Nacional de Ciencia y
Tecnolog\'{i}a through grant No. \textbf{256243} and C\'{a}tedras
Conacyt program 1577, and by DGAPA-PAPIIT UNAM under grant IN111119.
%\end{acknowledgments}

\bibliographystyle{unsrt}
\bibliography{Bibliografia}
\end{document}

@@

\bibitem{Lopez2003} C. L\'{o}pez, Materials aspects of photonic crystals,
\textit{Adv. Mater.} \textbf{15}, 1679--1704 (2003).

@@

\bibitem{Jena2019} S. Jena, R.B. Tokas, S. Tripathi, K.D. Rao, D.V. Udupa,
S. Thakur, N.K. Sahoo Influence of oxygen partial pressure on
microstructure, optical properties, residual stress and laser induced damage
threshold of amorphous HfO2 thin films \textit{Journal of Alloys and
Compounds}, Volume 771, 2019, pp. 373-381

@@

\bibitem{Canham1990} Canham L. T. Silicon quantum wire array fabrication by
electrochemical and chemical dissolution of wafers. \textit{Appl. Phys. Lett.%
}, 57(\textbf{10}):1046-1048, (1990).

\bibitem{Escorcia2007} Escorcia J. and Agarwal V. E ect of duty cycle and
frequency on the morphology of porous silicon formed by alternating square
pulse anodic etching. \textit{Phys. Status Solidi (c)}, 4(\textbf{6}%
):2039-2043, (2007).
